\large{\bf Looking forwards and backwards through locally regulated populations }

### 2023-01-24 forwards-and-backwards.tex
Update on Overleaf.

To make this precise, we must work in the vague topology. Proving tightness of the level process is slightly trickier as the levels of many particles will drift towards infinity in finite time. These particles however will not contribute to the metric associated with the vague topology and thus we will retain relative compactness. The main argument relies on the observation that particles with levels lower than some threshold $\overline{U}_{N, \delta}$  have regulated level increments of order $\epsilon$ over any small time interval of length $\delta t$ given large enough $N$. As a result, we can evaluate our level process against test functions $(g_n)_{n=1,..,N}$ with cut off smaller than $\overline{U}_{N, \delta}$.

@@

Then
$\{(U^{N}_{a}(t))_{t \geq \tau_a}, N >0\}$ is relatively compact in 
$\mathcal{D}_{[0,\infty]}[0,\infty )$, where $[0,\infty]$ is equipped with the metric $\mathfrak{d}$ for the vague topology in $[0,\infty]$ (see Theorem  \ref{Vague times Euclidean is Polish}).
\end{lemma}

@@

To control the level process, we consider two scenarios, one where the local density of the system between $[0,r]$ is never too big, i.e.
$$h(r)=\sup_{x \in \IR^d}\sup_{s\in [0,r]}\left\{\varrho_F*\eta^N_s(X^N_a(s)) \right\} \leq H_{\epsilon}(r),$$
and otherwise.

@@

\textbf{Introducing a cutoff range:} It suffices to show that for any $\epsilon > 0$ and for any line of descent $a \in \mathcal{U}$, there exists small enough  $\delta t>0$ such that $\mathbb{E}[\mathfrak{d}(U^{N}_{a}(t+\delta t),U^{N}_{a}(t))|{\cal F}_t^{
\eta}]< \epsilon$. \\
For this, pick $K_{\epsilon} \in \mathbb{N}$ such that $\frac{1}{2^{K_{\epsilon}}} < \epsilon/2$. then we have that 
\begin{equation}
\mathfrak{d}(U^{N}_{a}(t+\delta t),U^{N}_{a}(t))\leq  \sum_{n=1}^{K_{\epsilon}}\frac{1 \wedge |g_n(U^{N}_{a}(t+\delta t))-g_n(U^{N}_{a}(t))|}{2^n} +  \epsilon/2. 
\end{equation}
Now it suffices to prove that for small enough $\delta t>0$, $|g_n(U^{N}_{a}(t+\delta t))-g_n(U^{N}_{a}(t))| < \epsilon / (2K_{\epsilon})$.

Pick $\overline{U}_{K_{\epsilon}, \epsilon}>0$ large enough such that $\text{supp}(g_n)\subset [0,\overline{U}_{K_{\epsilon}, \epsilon}]$ for all $n=1,..,K_{\epsilon}$. Since we picked $g_n$ to be continuous and differentiable with compact support, by Mean Value Theorem we have that 
$$|g_n(U^{N}_{a}(t+\delta t ))-g_n(U^{N}_{a}(t))|<C_{g_1,..,g_{K_{\epsilon}}}(|U^{N}_{a}(t+\delta t)-U^{N}_{a}(t)|\wedge \overline{U}_{K_{\epsilon}, \epsilon}), $$
uniformly over $n=1,..,K_{\epsilon}$ for some constant $C'_{g_1,...,g_{K_{\epsilon}}}$. Note that it suffices to consider $|U^{N}_{a}(t+\delta t)-U^{N}_{a}(t)|\wedge \overline{U}_{K_{\epsilon}, \epsilon}$ because $g_n(u)=g_n(\overline{U}_{K_{\epsilon}, \epsilon})=0$ for all $u > \overline{U}_{K_{\epsilon}, \epsilon}$.

Therefore, it suffices to show that for all $\epsilon > 0$, there exists $\delta t>0$ small enough such that 
\begin{equation}
\mathbb{E}[C_{g_1,..,g_{K_{\epsilon}}}|U^{N}_{a}(t+\delta t)-U^{N}_{a}(t)|\wedge \overline{U}_{K_{\epsilon}, \epsilon} ~|~{\cal F}_t^{
\eta} ] < \epsilon /2    
\end{equation}
uniformly over $N \geq N_0$.

\textbf{Controlling high density events:}
Recall that in Lemma \ref{lem:eta_compact_containment}, we have established compact containment for the total mass process. Therefore for any $\epsilon>0$ and $r>0$, there exists some large 
\begin{equation}
    \label{eq: Mass Bound Constant}
H_{\epsilon}(r):=\frac{\epsilon}{2||\varrho_F||_{\infty}C(r) \overline{U}_{K_{\epsilon}}C_{g_1,..,g_{K_{\epsilon}}}}>0    
\end{equation}
such that 
the event 
$$A_{H_{\epsilon}}:= \left\{ \omega \in \Omega: \sup_{s\in [0,r]}\left\{\varrho_F*\eta^N_s(X^N_a(t+s)) \right\}(\omega) \geq H_{\epsilon}(r) \right\}$$
satisfies
\begin{equation}
\limsup_{N \to \infty}\mathbb{P}\left[A_{H_{\epsilon}}\right]
\leq  \frac{||\varrho_F||_{\infty}\mathbb{E}[\sup_{s\in [t,t+r]}\langle 1,  \eta^N_s \rangle ]}{H_{\epsilon}(r)}
\leq  \frac{||\varrho_F||_{\infty}C(t+r)}{H_{\epsilon}(r)}
< \frac{\epsilon}{2 \overline{U}_{K_{\epsilon}}C_{g_1,..,g_{K_{\epsilon}}}},
\end{equation}
where $(C(t))_{t \geq 0}$ is the growth function that bounds the expected value of the running supremum of the total mass in Equation \eqref{eqn:eta_mass_bound}.

As a result, for any $s < r$,
\begin{equation}
\begin{aligned}
\mathbb{E}\left[\mathfrak{d}(U^{N}_{a}(t+s),U^{N}_{a}(t)) : A_{H_{\epsilon}} ~|~{\cal F}_t^{
\eta} \right] & \leq  
  \mathbb{E}\left[\sum_{n=1}^{K_{\epsilon}}\frac{1 \wedge |g_n(U^{N}_{a}(t+s))-g_n(U^{N}_{a}(t))|}{2^n} +  \epsilon/2: A_{H_{\epsilon}} ~\bigg|~{\cal F}_t^{
\eta} \right]  \\
 & \leq  \sum_{n=1}^{K_{\epsilon}}\frac{\mathbb{E}\left[C_{g_1,..,g_{K_{\epsilon}}} \overline{U}_{K_{\epsilon}, \epsilon}: A_{H_{\epsilon}} \right] }{2^n} +  \epsilon/2  \\
& \leq  \sum_{n=1}^{K_{\epsilon}}\frac{C_{g_1,..,g_{K_{\epsilon}}} \overline{U}_{K_{\epsilon}, \epsilon}\mathbb{P}\left[ A_{H_{\epsilon}} \right] }{2^n} +  \epsilon/2 \\
& \leq  \sum_{n=1}^{K_{\epsilon}}\frac{\epsilon /2 }{2^n} +  \epsilon/2 \\
& < \epsilon.
\end{aligned}
\end{equation}

\textbf{Controlling bounded density events:}
We now consider $A_{H_{\epsilon}}^{c}$.
To control the downward drift of our levels from the quadratic evolution,
we neglect all positive drift and obtain
\begin{equation}
\begin{aligned}
\mathbb{E}[U^{N}_{a}(t+r)-U^{N}_{a}(t)] \geq   &   - \mathbb{E}\left[\int_{t}^{(t+r)  } b_{\theta}(X^N_a(s),\eta^N_s) U^N_a(s)ds\right]\\
\geq& - rC_G\overline{U}_{K_{\epsilon}, \epsilon}.
\end{aligned}    
\end{equation}

We can also control the upward drift by comparing our process $(U^N_{a}(\tau_a+r))_{r \geq 0}$ with another process $(W^N_a(r))_{r \geq 0}$, where 
\begin{align*}
&W^{N}_{a}(r)-W^{N}_{a}(0)\\
=&\int_{0}^{r}
\left(
        \frac{\theta}{N} C_G W^N_a(s)^2
        +
        C_F H_{\epsilon}(r) W^N_a(s)
    \right)
    ds,
\end{align*}
with $H_{\epsilon}(r) > \sup_{s\in [0,r]}\left\{\varrho_F*\eta^N_s(X^N_a(s)) \right\}$,
and $W^N_a(0)=U^N_a(\tau_a) = U_0 \leq \overline{U}_{K_{\epsilon}, \epsilon}$.

@@

Note that $(W^N_a(s))_{s \geq 0}$ can be solved explicitly and 
\begin{equation}
W^N_a(s) = \frac{C_F H_{\epsilon}(r) U_0 \exp(C_F H_{\epsilon}(r) s)}{C_F H_{\epsilon}(r)+C_G  N^{-1}\theta U_0(1- \exp(C_F H_{\epsilon}(r) s))}\leq \overline{U}_{K_{\epsilon}, \epsilon}    
\end{equation}
for 
\begin{equation}
    \label{eq: Bound on Level Hitting Time}
s \leq  \frac{1}{C_F H_{\epsilon}(r)} \log\left\{
1+
\frac{C_F H_{\epsilon}(r)
(\overline{U}_{K_{\epsilon}, \epsilon}
-U_0)
}
{C_F H_{\epsilon}(r)U_0 +C_G  N^{-1}\theta \overline{U}_{K_{\epsilon}, \epsilon}    U_0}
\right\}.
\end{equation}
As $\theta / N $ converges in the limit, we may take some constant $A$ such that for large enough $N$,
the level process $(U^N_{a}(s))_{s \geq 0}$ will not hit  $\overline{U}_{K_{\epsilon}, \epsilon}$ as long as
\begin{equation}
s \leq  \frac{1}{C_F H_{\epsilon}(r)} \log\left\{
1+
\frac{C_F H_{\epsilon}(r)
(\overline{U}_{K_{\epsilon}, \epsilon}
-U_0)
}
{C_F H_{\epsilon}(r)U_0 +C_G  A \overline{U}_{K_{\epsilon},\epsilon}    U_0}
\right\}:=T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r).
\end{equation}

Note that $T$ only depends on the initial level $U_0$, the upper limit $\overline{U}_{K_{\epsilon}, \epsilon}$ and the bound on total mass $C(r)$ at time $r$, and is independent to $N$. 
In particular, 
\begin{equation}
\label{eq: Compact Containment for Levels}
\limsup_{N \to \infty}
\mathbb{P}\left[
\sup_{t \in [0, T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r)]}
U^N_{a}(\tau_a + t)
\geq \overline{U}_{K_{\epsilon},\epsilon} 
\right]  
\leq \mathbb{P}[A_{H_{\epsilon}}]
< \frac{\epsilon}{2 \overline{U}_{K_{\epsilon}}C_{g_1,..,g_{K_{\epsilon}}}},
\end{equation}
so we have therefore proven compact containment condition for our level process up to time $T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r)$.

As a result, for all time $ 0 < t , t+ \delta t \leq T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r),$

\begin{align*}
W^N_a(t+\delta t)-W^N_a(t) 
\leq &\int_{t}^{t+\delta t} 
        \left( \frac{\theta}{N} C_G \overline{U}_{K_{\epsilon}, \epsilon}^2
        +
        C_F H_{\epsilon}(r) \overline{U}_{K_{\epsilon}, \epsilon}
        \right)
        ds\\
=&\left( \frac{\theta}{N} C_G \overline{U}_{K_{\epsilon}, \epsilon}^2
        +
        C_F H_{\epsilon}(r) \overline{U}_{K_{\epsilon}, \epsilon}
        \right) \delta t \\
\leq&\left( A C_G \overline{U}_{K_{\epsilon}, \epsilon}^2
        +
        C_F H_{\epsilon}(r) \overline{U}_{K_{\epsilon}, \epsilon}
        \right) \delta t
\end{align*}

Combining the results together, we have that for any $\delta t > 0$ small enough such that 
\begin{equation}
\delta t < \frac{\epsilon  }{4C_{g_1,..,g_{K_{\epsilon}}}}\min\left\{\frac{1}{C_G \overline{U}_{K_{\epsilon}, \epsilon}}, \frac{1}{A C_G \overline{U}_{K_{\epsilon}, \epsilon}^2
        +
        C_F H_{\epsilon}(r) \overline{U}_{K_{\epsilon}, \epsilon}}\right\}    
\end{equation}
holds, then we have for all $t \leq T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r)$,
\begin{equation}
\begin{aligned}
\mathbb{E}\left[\mathfrak{d}(U^{N}_{a}(t+\delta t),U^{N}_{a}(t)) : A_{H_{\epsilon}}^{c} \right] \leq  &  
  \mathbb{E}\left[\sum_{n=1}^{K_{\epsilon}}\frac{1 \wedge |g_n(U^{N}_{a}(t+\delta t))-g_n(U^{N}_{a}(t))|}{2^n} +  \epsilon/2: A_{H_{\epsilon}}^{c} ~\bigg|~{\cal F}_t^{
\eta}\right]  \\
 \leq &   \sum_{n=1}^{K_{\epsilon}}\frac{\mathbb{E}\left[C_{g_1,..,g_{K_{\epsilon}}} |U^{N}_{a}(t+r)-U^{N}_{a}(t)|: A_{H_{\epsilon}}^{c} ~\bigg|~{\cal F}_t^{
\eta} \right] }{2^n} +  \epsilon/2  \\
\leq&   \sum_{n=1}^{K_{\epsilon}}\frac{\mathbb{E}\left[C_{g_1,..,g_{K_{\epsilon}}} |C_G \overline{U}_{K_{\epsilon}, \epsilon} \delta t|  : A_{H_{\epsilon}}^{c} ~\bigg|~{\cal F}_t^{
\eta} \right] }{2^n}  \\
 & + \sum_{n=1}^{K_{\epsilon}}\frac{\mathbb{E}\left[C_{g_1,..,g_{K_{\epsilon}}}  |W^N_a(t+\delta t)-W^N_a(t)|: A_{H_{\epsilon}}^{c} ~\bigg|~{\cal F}_t^{
\eta} \right] }{2^n} +  \epsilon/2  \\
\leq  &  \sum_{n=1}^{K_{\epsilon}}\frac{\epsilon /2 }{2^n} +  \epsilon/2 \\
< &  \epsilon.
\end{aligned}
\end{equation}

@@

We have proven that for all $t \in [0, T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r)]$,
\begin{equation}
\begin{aligned}
\mathbb{E}[\mathfrak{d}(U^{N}_{a}(t+\delta t),U^{N}_{a}(t))~|~{\cal F}_t^{
\eta}] \leq & \mathbb{E}\left[\mathfrak{d}(U^{N}_{a}(t+\delta t),U^{N}_{a}(t)) : A_{H_{\epsilon}} ~|~{\cal F}_t^{
\eta}\right]\\
&+ \mathbb{E}\left[\mathfrak{d}(U^{N}_{a}(t+\delta t),U^{N}_{a}(t)) : A_{H_{\epsilon}}^{c} ~|~{\cal F}_t^{
\eta}\right] \\
< & \epsilon + \epsilon = 2\epsilon
\end{aligned}    
\end{equation}
for  
\begin{equation*}
\delta t < \frac{\epsilon  }{4C_{g_1,..,g_{K_{\epsilon}}}}\min\left\{\frac{1}{C_G \overline{U}_{K_{\epsilon}, \epsilon}}, \frac{1}{A C_G \overline{U}_{K_{\epsilon}, \epsilon}^2
        +
        C_F H_{\epsilon}(r) \overline{U}_{K_{\epsilon}, \epsilon}}\right\}.    
\end{equation*}

@@

\subsection{Tightness of the Lookdown Representation}
\begin{lemma}
The lookdown representation satisfies
Equation \eqref{eq: vague compact containment condition}, i.e.
for all $\epsilon>0$, there exists $N>0$ such that
\begin{equation}
 \limsup_{n \to \infty} \mathbb{P}\left\{ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle > N \right\} < \epsilon,
\end{equation}
\end{lemma}

\begin{proof}
For every $f \in C^{+}_{c}(\overline{\mathbb{R}^d} \times [0,\infty))$,
there exists $u^* > 0$ such that $f(x,u) = 0$ for all $u \geq u^*$.
Then,
\begin{equation}
\begin{aligned}
 &\limsup_{n \to \infty} \mathbb{P}\left\{ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle > N \right\} \\
 \leq & \limsup_{n \to \infty}\frac{\mathbb{E}\left\{ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle \right\}}{N}\\
 \leq & \limsup_{n \to \infty}||f||_{\infty}\frac{\mathbb{E}\left\{ \sup_{t\in [0,T]}\langle 1_{[0,u^*]}, \xi^n_t \rangle \right\}}{N}.
\end{aligned}
\end{equation}
Recall that conditional on 
$$ \frac{1}{n}\langle 1_{[0,n]}, \xi^n_t \rangle = \eta^n_t,$$
the level of each individual is independently and uniformly distributed between $[0,n]$.
Therefore, 
\begin{equation}
\mathbb{E}\left\{ \sup_{t\in [0,T]}\langle 1_{[0,u^*]}, \xi^n_t \rangle \right\} = u^* \mathbb{E}\left\{ \sup_{t\in [0,T]}\langle 1, \eta^n_t \rangle \right\}.
\end{equation}
Finally, 
recall that the supremum of the empirical measure process is controlled in Lemma \ref{lem:eta_compact_containment}
so there exists some constant $C_T$ such that 
\begin{equation}
\begin{aligned}
 &\limsup_{n \to \infty} \mathbb{P}\left\{ \sup_{t\in [0,T]}\langle f, \xi^n_t \rangle > N \right\} \\
 \leq & \limsup_{n \to \infty}||f||_{\infty}\frac{u^*}{N}\mathbb{E}\left\{ \sup_{t\in [0,T]}\langle 1, \eta^n_t \rangle \right\}\\
 \leq & ||f||_{\infty}\frac{u^*}{N}C_T\\
 < & \epsilon
\end{aligned}
\end{equation}
for sufficiently large $N$.
\end{proof}

@@

Recall that
the lookdown representation has a spatial component and a level component.
Specifically, for fixed $N>0$ and $t>0$,
the lookdown representation $\xi^N(t)$ 
is a finite measure on $\overline{\mathbb{R}^d} \times [0,N]$.

To characterise convergence of $\xi^N(t)$ as $N \to \infty$,
we therefore need to impose an appropriate topology on $\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty))$,
the space of finite measures on $\overline{\mathbb{R}^d} \times [0,\infty)$.

We now refer to the vague topology introduced in P564, \S A2 in \cite{kallenberg1997foundations}.
Let $S$ be a locally compact Polish space and $\hat{S}$ be the class of bounded sets in $S$.
We consider the family $C^{+}_c(S)$ of positive continuous functions with compact support. It is known that $C^{+}_c$ is separable in the uniform metric.
We now consider $\mathcal{M}(S)$, the class of measures on $S$ that are locally finite.
The \textit{vague topology} on $\mathcal{M}(S)$ is generated by the the maps $\mu \to \mu f := \int f d \mu$, where $f\in C^{+}_{c}(S)$.
In other words, convergence of $\mu^n \to \mu$ in the vague topology holds if 
$$\int f d\mu^n \to \int f d\mu$$
for all $f\in C^{+}_{c}(S)$.

>>>>

To make this precise, we must work in the vague topology. Proving tightness of the level process is slightly trickier as the levels of many particles will drift towards infinity in finite time. These particles however will not contribute to the metric associated with the vague topology and thus we will retain relative compactness. The main argument relies on the observation that particles with levels lower than some threshold $\overline{U}_{N, \delta}$  have regulated level increments of order $\epsilon$ over any small time interval of length $r$ given large enough $N$. As a result, we can evaluate our level process against test functions $(g_n)_{n=1,..,N}$ with cut off smaller than $\overline{U}_{N, \delta}$.

@@

Then
$\{(U^{N}_{a}(t))_{t \geq \tau_a}, N >0\}$ is relatively compact in 
$\mathcal{D}_{[0,\infty)}[0,\infty )$, where $[0,\infty)$ is equipped with the vague topology.
\end{lemma}

@@

To control the level process, we consider two scenarios, one where the local density of the system between $[0,r]$ is never too big, i.e.
$$h(r)=\sup_{x \in \IR^d}\sup_{s\in [0,r]}\left\{\varrho_F*\eta^N_s(x) \right\} \leq H_{\epsilon}(r),$$
and otherwise.

@@

\textbf{Introducing a cutoff range:} 
By the characterisation of vague topology on $[0,\infty)$,
it suffices to prove that for all functions $g\in C_{c}([0,\infty), \mathbb{R}])$ (continuous functions with compact support), 
the real-valued process
$\{(g(U^{N}_{a}(t)))_{t \geq \tau_a}, N >0\}$ is relatively compact in 
$\mathcal{D}_{\mathbb{R}}[0,\infty)$,
where $\mathbb{R}$ is equipped with the Euclidean metric.

It suffices to show that for any $\epsilon > 0$ and for any line of descent $a \in \mathcal{U}$, there exists small enough  $r>0$ such that $\mathbb{E}[|g(U^{N}_{a}(t+r))-g(U^{N}_{a}(t))||{\cal F}_t^{
\eta}]< \epsilon$.

Pick $U_{g,\varepsilon}>0$ large enough such that $\text{supp}(g)\subset [0,U_{g,\varepsilon}]$.
Since we picked $g$ to be continuous and differentiable with compact support, by Mean Value Theorem we have that 
$$|g(U^{N}_{a}(t+r ))-g(U^{N}_{a}(t))|<C'_{g}(|U^{N}_{a}(t+r)-U^{N}_{a}(t)|\wedge U_{g,\varepsilon}),$$
for some constant $C'_g$. Note that it suffices to consider $|U^{N}_{a}(t+r)-U^{N}_{a}(t)|\wedge U_{g,\varepsilon}$ because $g_n(u)=g_n(U_{g,\varepsilon})=0$ for all $u > U_{g,\varepsilon}$.

Therefore, it suffices to show that for all $\epsilon > 0$, there exists $r>0$ small enough and $N_0$ large enough such that 
\begin{equation}
\mathbb{E}[C'_{g}(|U^{N}_{a}(t+r)-U^{N}_{a}(t)|\wedge U_{g,\varepsilon}) ~|~{\cal F}_t^{
\eta} ] < \epsilon /2    
\end{equation}
uniformly over $N \geq N_0$.

\textbf{Controlling high density events:}
Recall that in Lemma \ref{lem:eta_compact_containment}, we have established compact containment for the total mass process. Therefore for any $\epsilon>0$ and $r>0$, there exists some large 
\begin{equation}
    \label{eq: Mass Bound Constant}
H_{\epsilon}(r):=\frac{\epsilon}{2||\varrho_F||_{\infty}C(r) }>0    
\end{equation}
such that 
the event 
$$A_{H_{\epsilon}}:= \left\{ \omega \in \Omega: \sup_{s\in [0,r]}\left\{\varrho_F*\eta^N_s(X^N_a(t+s)) \right\}(\omega) \geq H_{\epsilon}(r) \right\}$$
satisfies
\begin{equation}
\limsup_{N \to \infty}\mathbb{P}\left[A_{H_{\epsilon}}\right]
\leq  \frac{||\varrho_F||_{\infty}\mathbb{E}[\sup_{s\in [t,t+r]}\langle 1,  \eta^N_s \rangle ]}{H_{\epsilon}(r)}
\leq  \frac{||\varrho_F||_{\infty}C(t+r)}{H_{\epsilon}(r)}
< \frac{\epsilon}{2 U_{g,\varepsilon}C'_g},
\end{equation}
where $(C(t))_{t \geq 0}$ is the growth function that bounds the expected value of the running supremum of the total mass in Equation \eqref{eqn:eta_mass_bound}.

As a result, for any $s < r$,
\begin{equation}
\mathbb{E}\left[|g(U^{N}_{a}(t+r ))-g(U^{N}_{a}(t))| \mathbbm{1}_{A_{H_{\epsilon}}} ~|~{\cal F}_t^{
\eta} \right] 
\leq  \mathbb{E}\left[C'_{g} U_{g,\varepsilon}\mathbbm{1}_{A_{H_{\epsilon}}} \right] \leq  C'_{g} U_{g,\varepsilon}\mathbb{P}\left[A_{H_{\epsilon}} \right] < \varepsilon / 2.
\end{equation}

\textbf{Controlling bounded density events:}
We now consider $A_{H_{\epsilon}}^{c}$.
To control the downward drift of our levels from the quadratic evolution,
we neglect all positive drift and obtain
\begin{equation}
\begin{aligned}
\mathbb{E}[U^{N}_{a}(t+r)-U^{N}_{a}(t)] \geq   &   - \mathbb{E}\left[\int_{t}^{(t+r)  } b_{\theta}(X^N_a(s),\eta^N_s) U^N_a(s)ds\right]\\
\geq& - rC_GU_{g,\varepsilon}.
\end{aligned}    
\end{equation}

We can also control the upward drift by comparing our process $(U^N_{a}(\tau_a+r))_{r \geq 0}$ with another process $(W^N_a(r))_{r \geq 0}$, where 
\begin{align*}
&W^{N}_{a}(r)-W^{N}_{a}(0)\\
=&\int_{0}^{r}
\left(
        \frac{\theta}{N} C_G W^N_a(s)^2
        +
        C_F H_{\epsilon}(r) W^N_a(s)
    \right)
    ds,
\end{align*}
with $H_{\epsilon}(r) > \sup_{s\in [0,r]}\left\{\varrho_F*\eta^N_s(X^N_a(s)) \right\}$,
and $W^N_a(0)=U^N_a(\tau_a) = U_0 \leq U_{g,\varepsilon}$.

@@

Note that $(W^N_a(s))_{s \geq 0}$ can be solved explicitly and 
\begin{equation}
W^N_a(s) = \frac{C_F H_{\epsilon}(r) U_0 \exp(C_F H_{\epsilon}(r) s)}{C_F H_{\epsilon}(r)+C_G  N^{-1}\theta U_0(1- \exp(C_F H_{\epsilon}(r) s))}\leq U_{g,\varepsilon}    
\end{equation}
for 
\begin{equation}
    \label{eq: Bound on Level Hitting Time}
s \leq  \frac{1}{C_F H_{\epsilon}(r)} \log\left\{
1+
\frac{C_F H_{\epsilon}(r)
(U_{g,\varepsilon}
-U_0)
}
{C_F H_{\epsilon}(r)U_0 +C_G  N^{-1}\theta U_{g,\varepsilon}    U_0}
\right\}.
\end{equation}
As $\theta / N $ converges in the limit, we may take some constant $\bar{\alpha}$ such that for large enough $N$,
the level process $(U^N_{a}(s))_{s \geq 0}$ will not hit  $U_{g,\varepsilon}$ as long as
\begin{equation}
s \leq  \frac{1}{C_F H_{\epsilon}(r)} \log\left\{
1+
\frac{C_F H_{\epsilon}(r)
(U_{g,\varepsilon}
-U_0)
}
{C_F H_{\epsilon}(r)U_0 +C_G  \bar{\alpha} \overline{U}_{K_{\epsilon},\epsilon}    U_0}
\right\}:=T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r).
\end{equation}

Note that $T$ only depends on the initial level $U_0$, the upper limit $U_{g,\varepsilon}$ and the bound on total mass $C(r)$ at time $r$, and is independent to $N$. 
In particular, 
\begin{equation}
\label{eq: Compact Containment for Levels}
\limsup_{N \to \infty}
\mathbb{P}\left[
\sup_{t \in [0, T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r)]}
U^N_{a}(\tau_a + t)
\geq \overline{U}_{K_{\epsilon},\epsilon} 
\right]  
\leq \mathbb{P}[A_{H_{\epsilon}}]
< \frac{\epsilon}{2 U_{g,\varepsilon}C'_g},
\end{equation}
so we have therefore proven compact containment condition for our level process up to time $T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r)$.

As a result, for all time $ 0 < t , t+ r \leq T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r),$

\begin{align*}
W^N_a(t+r)-W^N_a(t) 
\leq &\int_{t}^{t+r} 
        \left( \frac{\theta}{N} C_G U_{g,\varepsilon}^2
        +
        C_F H_{\epsilon}(r) U_{g,\varepsilon}
        \right)
        ds\\
=&\left( \frac{\theta}{N} C_G U_{g,\varepsilon}^2
        +
        C_F H_{\epsilon}(r) U_{g,\varepsilon}
        \right) r \\
\leq&\left( \bar{\alpha} C_G U_{g,\varepsilon}^2
        +
        C_F H_{\epsilon}(r) U_{g,\varepsilon}
        \right) r
\end{align*}

Combining the results together, we have that for any $r > 0$ small enough such that 
\begin{equation}
r < \frac{\epsilon  }{4C'_g}\min\left\{\frac{1}{C_G U_{g,\varepsilon}}, \frac{1}{\bar{\alpha} C_G U_{g,\varepsilon}^2
        +
        C_F H_{\epsilon}(r) U_{g,\varepsilon}}\right\}    
\end{equation}
holds, then we have for all $t \leq T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r)$,

\begin{equation}
\begin{aligned}
\mathbb{E}\left[|g(U^{N}_{a}(t+r ))-g(U^{N}_{a}(t))| \mathbbm{1}_{A_{H_{\epsilon}}^c} ~|~{\cal F}_t^{
\eta} \right] 
& \leq  \mathbb{E}\left[C'_{g} |U^{N}_{a}(t+r )-U^{N}_{a}(t)|\mathbbm{1}_{A_{H_{\epsilon}}^c} \right] \\
&\leq r C'_g \max\{ \bar{\alpha} C_G U_{g,\varepsilon}^2
        +
        C_F H_{\epsilon}(r) U_{g,\varepsilon}
        , C_G U_{g, \varepsilon}\} \\
        & < \varepsilon.
\end{aligned}
\end{equation}

@@

We have proven that for all $t \in [0, T(U_0,\overline{U}_{K_{\epsilon},\epsilon},r)]$,
\begin{equation}
\begin{aligned}
& \mathbb{E}[|g(U^{N}_{a}(t+r ))-g(U^{N}_{a}(t))|~|~{\cal F}_t^{
\eta}]\\
\leq & \mathbb{E}\left[|g(U^{N}_{a}(t+r ))-g(U^{N}_{a}(t))| \mathbbm{1}_{A_{H_{\epsilon}}} ~|~{\cal F}_t^{
\eta}\right]+ \mathbb{E}\left[|g(U^{N}_{a}(t+r ))-g(U^{N}_{a}(t))| \mathbbm{1}_{A_{H_{\epsilon}}^c} ~|~{\cal F}_t^{
\eta}\right] \\
< & \epsilon + \epsilon = 2\epsilon
\end{aligned}    
\end{equation}
for  
\begin{equation*}
r < \frac{\epsilon  }{4C'_g}\min\left\{\frac{1}{C_G U_{g,\varepsilon}}, \frac{1}{\bar{\alpha} C_G U_{g,\varepsilon}^2
        +
        C_F H_{\epsilon}(r) U_{g,\varepsilon}}\right\}.    
\end{equation*}

@@

\subsection{Tightness of the Lookdown Representation}
\begin{lemma}
The lookdown representation satisfies the compact containment condition, 
Equation \eqref{eq: vague compact containment condition}, 
for all $\varepsilon > 0$ and fixed time $T > 0$, there exists $N,K> 0$ such that 
\begin{equation}
\liminf_{n \to \infty}\mathbb{P}\{ \xi^n_t \in \Gamma_{N,K} \text{ for all } t\in [0,T]\} > 1-\varepsilon,
\end{equation}
where $\Gamma_{N,K}$ is the compact set in Lemma \ref{lem: vague compact sets}
\end{lemma}

\begin{proof}
Note that
\begin{equation}
\begin{aligned}
     &1-\mathbb{P}\{ \xi^n_t \in \Gamma_{N,K} \text{ for all } t\in [0,T]\} \\
     = & \mathbb{P}\left\{ \sup_{t \in[0,T]}\frac{1}{N}\langle 1_{\overline{\mathbb{R}^d}\times [0,N]}, \xi^n_t \rangle \geq K \right\} \\
 \leq & \frac{\mathbb{E}\left\{ \sup_{t \in[0,T]}\frac{1}{N}\langle 1_{\overline{\mathbb{R}^d}\times [0,N]}, \xi^n_t \rangle\right\}}{K}.
\end{aligned}
\end{equation}
Recall that conditional on 
$$ \frac{1}{n}\langle 1_{[0,n]}, \xi^n_t \rangle = \eta^n_t,$$
the level of each individual is independently and uniformly distributed between $[0,n]$.
Therefore, for $n \geq N$,
\begin{equation}
\frac{\mathbb{E}\left\{ \sup_{t \in[0,T]}\frac{1}{N}\langle 1_{\overline{\mathbb{R}^d}\times [0,N]}, \xi^n_t \rangle\right\}}{K}
= \frac{\mathbb{E}\left\{ \sup_{t\in [0,T]}\langle 1, \eta^n_t \rangle \right\}}{K} < \varepsilon,
\end{equation}
for large enough $K>0$. 
The last inequality is given by Lemma \ref{lem:eta_compact_containment}.
\end{proof}

@@

Recall that
the lookdown representation has a spatial component and a level component.
Specifically, for fixed $N>0$ and $t>0$,
the lookdown representation $\xi^N(t)$ 
is a finite measure on $\overline{\mathbb{R}^d} \times [0,N]$.
Furthermore, the level of a particle in our lookdown representation can shoot to infinity in finite time.
Therefore, to characterise convergence of $\xi^N(t)$ as $N \to \infty$,
we need to impose an appropriate vague topology on $\mathcal{M}(\overline{\mathbb{R}^d} \times [0,\infty))$,
the space of finite measures on $\overline{\mathbb{R}^d} \times [0,\infty)$.
Similarly, to characterise convergence of the level process of individual lineages, we consider the vague topology on $[0,\infty)$.

We now refer to the vague topology on measure spaces introduced in P564, \S A2 in \cite{kallenberg1997foundations}.
Let $S$ be a locally compact Polish space and $\hat{S}$ be the class of bounded sets in $S$.
We consider the family $C^{+}_c(S)$ of positive continuous functions with compact support. It is known that $C^{+}_c$ is separable in the uniform metric.
We now consider $\mathcal{M}(S)$, the class of measures on $S$ that are locally finite.
The \textit{vague topology} on $\mathcal{M}(S)$ is generated by the the maps $\mu \to \mu f := \int f d \mu$, where $f\in C^{+}_{c}(S)$.
In other words, convergence of $\mu^n \to \mu$ in the vague topology holds if 
$$\int f d\mu^n \to \int f d\mu$$
for all $f\in C^{+}_{c}(S)$.

We now introduce an important theorem on compactness in the vague topology.
\begin{theorem}[Theorem A.23 in \cite{kallenberg1997foundations}]
For any locally compact, second-countable Hausdorff Space $S$, 
we have
\begin{itemize}
\item $\mathcal{M}(S)$ is Polish in the vague topology,
\item a set $A\subset \mathcal{M}(S)$ is vaguely relatively compact iff $\sup_{\mu\in A} \mu f < \infty$ for all $f \in C^{+}_{c}$
\item if $\mu_n \to \mu$ in the vague topology and $B \in \hat{S}$ with $\mu \partial B = 0$, then $\mu_n B \to \mu B$
\end{itemize}
\end{theorem}

To characterise convergence of lookdown representations,
we take $S = \overline{\mathbb{R}^d} \times [0,\infty)$.
We now identify compact sets under the vague topologies.
